\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-09-27 challenge.tex
Challenge#3

However, there is a tension between extensibility of inductive types
and exhaustivity of induction reasoning.
In \cref{fig:stlc-nonmechanized}, all the lemmas and theorems, as well as
the substitution function, require induction reasoning.
A language design must enforce that induction remains exhaustive in the
derived family despite the new constructors, without requiring
redefinition or rechecking of those cases already handled by the base
family.
%
The tension reflects a duality between variants and records.
For record-like language constructs (e.g., classes and objects), it is
safe for an extension to add more fields: projection of existent fields
still works.
But variant-like constructs (e.g., inductive types) do not automatically
enjoy safe, modular addition of constructors:
pattern matching could potentially become non-exhaustive.

@@

Common to many family-polymorphism mechanisms is the ability for a
derived family to override fields defined in the base family.
As we show later, this expressiveness is also useful for metatheory
mechanization.
However, it is in conflict with dependent typing, wherein type checking
often involves unfolding definitions.
In \cref{fig:stlc-nonmechanized}, the proof of the substitution lemma is
checked against the definition of the substitution function.
If a derived family were allowed to arbitrarily override how
substitution is defined, then the proof, when inherited, would be
ill-formed.
A language design should only allow those overridings that are safe.

@@

@@

These three examples both show the incompatibility between exposing the
concrete definition of a field for reasoning (this second example even
involves the definition of fixpoint and pattern matching) and
overridability. We need to be careful about this tension when designing
the language.\YZ{
  The two examples seem to suggest there should not be any overriding allowed at all.
  Is there an example where you actually want the ability to override?
}\EDJreply{Added a new example. Please check.}

@@

\textlabel{Challenge (4)}{chg:software-engineering}~\textbf{Engineering and Ecosystem}.
Not only for the metatheory, we also want our implementation of family
to have good compatibility with the rest of Coq. For example, we
shouldn't compromise \textbf{tactic programming} as it is part of the
idiomatic Coq programming experience. Additionally, the interactive development
style requires \textbf{incremental type checking}---our design has to be
able to type check each Coq Vernacular command once inputted. What's
more, we want our family ``term'' to be incorporated into Coq \textbf{without
breaking its other functionality}. For example, the user may want to
project the family member anywhere inside an arbitrary Gallina term,
that may later be computed and normalized. However, families themselves
can be second class citizens just like \citet{zm2017}.\YZ{I was thinking
if the paper should start by talking about the functional encoding of
inheritance (namely exposing a self parameter to allow late binding, and
later taking the fixpoint of the extensible module when it needs to be
accessed outside the family).  I think most readers will benefit from a
recap of this encoding.\\
Coq is total but that doesn’t prevent Coq from having a Fixpoint keyword (plus you proved your language is consistent).
}\EDJreply{Feel free to add these. I don't have many knowledge about this part.}

>>>>

However, there is a tension between extensibility of inductive types
and exhaustivity of induction reasoning.
In \cref{fig:stlc-nonmechanized}, all the lemmas and theorems, as well as
the substitution function, require induction reasoning.
A language design must enforce that induction remains exhaustive in the
derived family despite the new constructors, without requiring
redefinition or rechecking of those cases already handled by the base
family.\footnote{%
The tension reflects a duality between variants and records.
For record-like language constructs (e.g., classes and objects), it is
safe for an extension to add more fields: existing fields can still be
projected.
But variant-like constructs (e.g., inductive types) do not automatically
enjoy safe, modular addition of constructors:
pattern matching could potentially become non-exhaustive.}

@@

Common to many family-polymorphism mechanisms is the ability for a
derived family to override fields defined in the base family.
As we show later, this expressiveness is also useful for metatheory
mechanization.
However, it is in conflict with dependent typing, wherein type checking
often involves unfolding definitions.
For example, in an STLC mechanization, the substitution lemma is checked
against the definition of the substitution function.
If a derived family were allowed to arbitrarily override the
substitution function, then the proof of the substitution lemma, when
inherited, would be ill-formed (even in the absence of any inductive-type extensions).
A language design should only allow those overridings that are safe.

@@

Inheritance and family polymorphism are mechanisms for
incrementally modifying self-referential definitions~\cite{cook1990inheritance}:
the implicit self parameterization is how they achieve late binding and thus extensibility.
However, self reference could easily lead to divergence.
Divergence is not a concern for the design of ordinary OO or
functional languages, but it means logical inconsistency---and
hence unsoundness---for a language aimed at logical reasoning.
A language design must ensure that the added extensibility does not
go rogue.

@@

These three examples both show the incompatibility between exposing the
concrete definition of a field for reasoning (this second example even
involves the definition of fixpoint and pattern matching) and
overridability. We need to be careful about this tension when designing
the language.

@@

\textlabel{Challenge (4)}{chg:software-engineering}~\textbf{Engineering and Ecosystem}.
Not only for the metatheory, we also want our implementation of family
to have good compatibility with the rest of Coq. For example, we
shouldn't compromise \textbf{tactic programming} as it is part of the
idiomatic Coq programming experience. Additionally, the interactive development
style requires \textbf{incremental type checking}---our design has to be
able to type check each Coq Vernacular command once inputted. What's
more, we want our family ``term'' to be incorporated into Coq \textbf{without
breaking its other functionality}. For example, the user may want to
project the family member anywhere inside an arbitrary Gallina term,
that may later be computed and normalized. However, families themselves
can be second class citizens just like \citet{zm2017}.
%\YZ{I was thinking
%if the paper should start by talking about the functional encoding of
%inheritance (namely exposing a self parameter to allow late binding, and
%later taking the fixpoint of the extensible module when it needs to be
%accessed outside the family).  I think most readers will benefit from a
%recap of this encoding.\\
%Coq is total but that doesn’t prevent Coq from having a Fixpoint keyword (plus you proved your language is consistent).
%}\EDJreply{Feel free to add these. I don't have many knowledge about this part.}
